Continuous time

### 2023-09-22 continuous-time.qmd
show quantiles

## Main model
Define a spline that uses 4 degrees of freedom.

```{r}
#| label: define-spline

ns4 <- function(x) {
  ns(
    x,
    knots = c(0.05, 0.33, 0.7),
    Boundary.knots = c(0, 3)
  )
}
```

>>>>

## Main model
Define a spline that uses 4 degrees of freedom. We base this on the quantiles of `hours`.

```{r}
#| label: spline-percentiles
quantile(dat$hours)
```

Not all participants contributed an equal number of observations. We'll calculate the max session length per participant.

```{r}
#| label: tbl-session-max-prop
#| tbl-cap: Proportion of participants that had at least on session last longer than gt_* hours
dat |> 
  summarize(
    max = max(hours), .by = c(pid)
  ) |> 
  summarise(
    gt_0.33 = mean(max > 0.33),
    gt_0.71 = mean(max > 0.716),
    gt_1 = mean(max > 1),
    gt_2 = mean(max > 2),
  ) |> 
  kable(digits = 2)
```

@tbl-session-max-prop shows that 66% of the participant have at least one session that lasted for over 0.71 hours. So we will base our knot placement on these quantiles.

```{r}
#| label: define-spline
ns4 <- function(x) {
  ns(
    x,
    knots = c(0.05, 0.33, 0.7),
    Boundary.knots = c(0, 3)
  )
}
```
